---
output: 
  github_document:
    html_preview: false
---

```{r, echo=FALSE}
knitr::opts_chunk$set(
  collapse = TRUE,
  comment = "#>"
  )
```

## Overview

`"Binomial" is an R package that implements functions for calculating probabilities of a Binomial random variable, and related calculations such as probability distribution, the expected value, variance, etc.


* `bin_distribution()` computes probability distribution for set amount of trials (of class `bindis`)
* `bin_cumulative()` computes probability distribution and cumulative probabilites for set amount of trials (of class `bincum`)
* `bin_variable()` creates an object of class `binvar` which can be passed into `summary.binvar()`  to make an object of class `summary.binvar`.  This object can be inspected with `summary()` methods.
*`plot()` creates plots of objects of either `bindis` (a probability distribution histogram) or `bincum` (a cumulative distribution line plot)

## Motivation

This package was developed for UC Berkeley's Statistics 133 Spring 2019 class in order to gain familiarity with package creation in R.

## Installation

Install the development version from GitHub via the package `"devtools"`:

```{r}
# development version from GitHub:
#install.packages("devtools") 

# install "binomial" (without vignettes)

devtools::install_github("stat133-sp19/hw-stat133-aliciakim/binomial")

# install "binomial" (with vignettes)

devtools::install_github("stat133-sp19/hw-stat133-aliciakim/binomial", build_vignettes = TRUE)
```

## Usage
```{r}
library(binomial)

bin_variable(trials=10, prob=0.5)

#ways 3 successes can occur in 10 trials
bin_choose(n=10, k=3)

#probability of getting 2 successes in 5 trials
bin_probability(success=2, trials=5, prob=0.5)

#create bindis object
bind1 <- bin_distribution(trials=10, prob=0.5)

#create bincum object
binc1 <- bin_cumulative(trials=10, prob=0.5)

#create binv object and get summary
binv1 <- bin_variable(trials=10, prob=0.5)
binv1

binv1sum <- summary(binv1)
binv1sum


#summary measures
bin_mean(trials=10, prob=0.5)
bin_variance(trials=10, prob=0.5)
bin_mode(trials=10,prob=0.5)
bin_skewness(trials=10,prob=0.5)
bin_kurtosis(trials=10,prob=0.5)
```

